---
title: "Accidents Analysis Across Italy"
format:
  html:
    theme: flatly
    code-fold: true
    toc: true
    number-sections: true
    code-copy: true
---

# Introduction

In this Report we are going to analyse the dataset accidents, which represents Six-monthly accident data across al Italy grouped by "region", with respect to the place of occurrence, and it is downloaded from [INAIL](https://dati.inail.it/opendata/elements1/DatiConCadenzaSemestraleInfortuniAbruzzo). The first step, we collect the data by region from INAIL website and merge the data into one dataset, the second step we create a package in R for the dataset (`accidentr` ). However, the dataset contains 25 variables and 3052056 observations, and variables can be grouped into 7 types as the following:

:::[.incremental]

***A - temporal location of the injury:***

:::{layout-ncol=1}
1. detection date: it is the date of extraction of the data (recorded and validated) from the archives; temporally qualifies the information base;
2. protocol date (of the case): it is the protocol date of the case;
3. date of occurrence: is the date on which the accident occurred;
4. date of definition: is the date of the prevailing administrative definition;
5. date of death: is the date of death of the injured party following an accident;
:::

***B - geographical location of the accident:***

:::{layout-ncol=1}
6. place of occurrence: is the ISTAT code of the province where the accident occurred;
:::


***C - characteristics of the injured person:***

:::{layout-ncol=1}
7. identification of the injured person: internal code (for longitudinal analysis);
8. gender: is the gender of the injured person;
9. age: the age of the injured party on the `date of occurrence`, expressed in years of age;
10. place of birth: cadastral code of the injured party's place of birth;
:::

***D - method of injury:***

:::{layout-ncol=1}
11. modality of occurrence: code of the modality (if `during work`, `in itinere`);
12. with / without means of transport (involved): mode code (if `with` or `without`);
:::

***E - administrative characteristics of the injury:***

:::{layout-ncol=1}
13. case identifier: internal code (for longitudinal analyzes);
14. administrative definition: code that characterizes the administrative situation of the accident case (if `positive` or `negative`) or the `exempt` outcome or the `preliminary investigation` situation;
15. administrative definition of the fatal outcome: code that characterizes the administrative situation of the case of an accident with a fatal outcome (if `positive` or `negative`) or the situation `in investigation`;
16. indemnity: code of the type of indemnity (if `temporary`, `capital`, `direct annuity`, `survivors' annuity`);
17. cause of negativity for the fatal outcome: code of the cause for which the case of an accident with a fatal outcome is defined as negative (if "activity not protected", for "lack of valid documentation", if for "lack of itinere ", for" lack of condition during work ", if for" fatal outcome not attributable to the event ", if" unprotected person ", if for" other causes of negativity ");
:::

***F - medico-legal characteristics of the accident:***

:::{layout-ncol=1}
18. degree of impairment: overall degree of impairment of the psychophysical integrity of the injured person;
19. days indemnified: number of days indemnified;
:::

***G - characteristics of the employer:***

:::{layout-ncol=1}
20. employer: internal identification code of the employer (for longitudinal analyzes);
21. territorial insurance position: internal code;
22. sector of economic activity: this is the primary ATECO code of the insurer;
23. management: if `agriculture`, `industry and services`, `on behalf of the state`;
24. tariff management: if `industry`, `crafts`, `tertiary`, `other activities`;
25. large tariff group: code of the large tariff group (whether `agricultural processing and food`,`chemical, paper and leather`, `construction and plant`, `energy and communications`, `wood and similar`, `metals and machinery`;` rock and glass mining `,` textiles and packaging `,
`transport and warehouses `,` various activities `).


:::

:::

*Required Libraries*

:::[.incremental]

* accidentr
* ggplot
* dplyr
* scales
* tidyr
* treemapify
* plotly

:::

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(accidentr)
library(ggplot2)
library(plotly)
library(dplyr)
library(scales)
library(tidyr)
library(treemapify)
library(reactable)
library(ltm)
```

*Load the data*
```{r}
data(Ita_Regions)
```

*overview of the data*
```{r}
str(Ita_Regions)
```


*Check for missing values*
```{r, results='hide'}
sapply(Ita_Regions, function(x) sum(is.na(x)))
```
*Check for unique values in every columns*
```{r, results='hide'}
sapply(Ita_Regions, function(x) length(unique(x)))
```



*Extract the number of accidents everyday*

```{r}
dataACC <- Ita_Regions %>%  
  count(DataAccadimento) %>%
  #summarise(n = sum(n)) %>%
  #mutate(dat = as.Date(DataAccadimento, format = "%m/%d/%Y"))  
  group_by(DataAccadimento)
#dataACC
```

*Exreact the day, month and year*

```{r}
data2 <- dataACC
data2$Date_Time <- strptime(data2$DataAccadimento, format = "%d/%m/%Y")
data2$Day <- format(data2$Date_Time, "%d")
data2$Month <- format(data2$Date_Time, "%m")
data2$NameMonth <- format(data2$Date_Time, "%b")
data2$Year <- format(data2$Date_Time, "%Y")

```

# Data Visualization

## The number of accidents by year
*aggregate number of accidents by year*
```{r}
mydata_total <- data2 %>% 
  group_by(Year) %>%
  summarise(total = sum(n)) %>%
  as.data.frame()
write.csv(mydata_total, "index.csv", row.names = FALSE)
```

```{r}
reactable(
  mydata_total,
  columns = list(
    Year = colDef(name = "Years"),
    total= colDef(name = "Total of accidents")
  )
)
```


```{r}
ggplot(mydata_total, 
       aes(x = Year, 
           y = total)) +
  geom_line(size = 1.5, 
            color = "lightgrey") +
  geom_point(size = 3, 
             color = "steelblue") +
  theme_minimal() +
  labs(y = "Number of Accidents (years)", 
       x = "Year",
       title = "Number of Accidents changes over time",
       subtitle = "Italy (2017-2021)",
       caption = "Source:          https://dati.inail.it/opendata/default/Infortuni/index.html")

```
From the graph we can tell that, 2017 has the highest rate of accidents while 2021 has the lowest rate of accidents. However, the frequency of accidents has decreased dramatically by -11.18% in 2020 form 2019 and this is quit reasonable due to the pandemic (Covid 19), and the frequent of accident has declined from 2020 to 2021 by -1.47. In general, the frequency of accidents is showing a declining trend over the 5 years period except the year 2019 there was an increase by 0.081 from the year 2018.

### Index of accidents

```{r}
Index <- read.csv("index.csv")
Index$Num_Wks <- c(16518031, 16911409, 17336533, 15960796, 17146622)
Index$accident_Indx <- round((Index$total/Index$Num_Wks)*100, 4)
#Index
```

```{r}
reactable(
  Index,
  columns = list(
    Year = colDef(name = "Years"),
    total= colDef(name = "Total of accidents"),
    Num_Wks = colDef(name = "Number of workers"),
    accident_Indx = colDef(name = "Accident Index")
  )
)
```

```{r}
colors = c("Index" ="blue")
ggplot(Index, aes(x = Year)) + 
  geom_line(aes(y = accident_Indx, color = "Index"), size = 0.5) +
  labs(x = "Years",
         y = "Percentage of accidents ",
         color = "Legend") +
  scale_color_manual(values = colors) +
  theme_minimal()
  
```
The graph illustrate the index of accidents `(Number of accidents/Number of workers)` in yearly bases, from the graph we can see that the index of accidents have a downward trend over the years, with 3.89% at the year 2017 and 3.27% at the year 2021 which shows that this percentage of the accidents has declined by 0.62%. 

## The number of accidents by months

*Aggregate number of accidents by month spread across the years*
```{r}
mydata <- data2 %>% 
  group_by(Year, Month, NameMonth) %>%
  summarise(total = sum(n)) %>%
  spread(key = "Year", value = total) %>%
  as.data.frame()
#mydata
```
```{r}
colnames(mydata) <- c("Month", "NameMonth", "Year2017", "Year2018", "Year2019",
                      "Year2020", "Year2021")
write.csv(mydata, "df.csv")
df <- read.csv("df.csv")
```

```{r}
reactable(
  df[,-1]
)
```


```{r}
colors = c("Year 2017" ="red","Year 2018"= "blue",
           "Year 2019" ="green","Year 2020"= "orange","Year 2021" = "black")
ggplot(df, aes(x = Month)) + 
  geom_line(aes(y = Year2017, color = "Year 2017"), size = 0.5) +
  geom_line(aes(y = Year2018, color = "Year 2018"), size = 0.5) +
  geom_line(aes(y = Year2019, color = "Year 2019"), size = 0.5) +
  geom_line(aes(y = Year2020, color = "Year 2020"), size = 0.5) +
  geom_line(aes(y = Year2021, color = "Year 2021"), size = 0.5) +
  labs(x = "Months",
         y = "number of accidents",
         color = "Legend") +
  scale_color_manual(values = colors) +
  xlim(1,12) +
  theme_minimal()
  
```
From the graph we can see that, the number of accidents around summer is always lower with respect to other seasons. However, after summer there is a dramatic increase in the number of accidents across Italy. Furthermore, we noticed as well there are three peeks in the year except for the year 2020, the peeks are around March, May and October. Considering the years of the pandemic, in March of 2020 the number of accidents declined sharply and hit the lowest value in May 2020 and in the same year the number of accidents hits the peek around November and this is the highest number of accidents recorded with respect to the other years. 



## The porportion between male and female accident

The number of accidents occurring to male is about double the number of accident for females, and this result is reasonable because most of the desirous job are performed by male. 

```{r}
Gender <- Ita_Regions %>%
  count(Genere) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(Gender, 
       aes(x = reorder(Genere, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Genere", 
       y = "Percent", 
       title  = "Participants by Genere")
```

```{r}
ggplot(Ita_Regions, 
       aes(x = Eta, 
           fill = Genere)) +
  geom_density(alpha = 0.4) +
  labs(title = "Age distribution by Gender") +
  theme_minimal()
```


From the figure above, we can see that accidents among female workers is at the hihgest rate around the ages 30, 40 and 50, while the age with most frequent accidents among male workers is around the ages 40, 50 and 60. However, at ages from 20 -30 the frequency of accidents for the female workers is higher than male, while at the ages lower than 20 the accidents rate is higher among male workers with respect to female workers. For ages greater than 40 till 60 the accidents is higher for male compared to female.

## Modality of occurrence

```{r}
# create a pie chart with slice labels
Mod_acc <- Ita_Regions %>%
  count(ModalitaAccadimento) %>%
  arrange(desc(ModalitaAccadimento)) %>%
  mutate(prop = round(n*100/sum(n), 1),
         lab.ypos = cumsum(prop) - 0.5*prop)

Mod_acc$label <- paste0(Mod_acc$ModalitaAccadimento, "\n",
                         round(Mod_acc$prop), "%")

ggplot(Mod_acc, 
       aes(x = "", 
           y = prop, 
           fill = ModalitaAccadimento)) +
  geom_bar(width = 1, 
           stat = "identity", 
           color = "black") +
  geom_text(aes(y = lab.ypos, label = label), 
            color = "black") +
  coord_polar("y", 
              start = 0, 
              direction = -1) +
  theme_void() +
  theme(legend.position = "FALSE") +
  labs(title = "Accidents by Modality of occurrence")
```

## Accidents with and without means of transport

```{r}
# create a pie chart with slice labels
Mod <- Ita_Regions %>%
  count(ConSenzaMezzoTrasporto) %>%
  arrange(desc(ConSenzaMezzoTrasporto)) %>%
  mutate(prop = round(n*100/sum(n), 1),
         lab.ypos = cumsum(prop) - 0.5*prop)

Mod$label <- paste0(Mod$ConSenzaMezzoTrasporto, "\n",
                         round(Mod$prop), "%")

ggplot(Mod, 
       aes(x = "", 
           y = prop, 
           fill = ConSenzaMezzoTrasporto)) +
  geom_bar(width = 1, 
           stat = "identity", 
           color = "black") +
  geom_text(aes(y = lab.ypos, label = label), 
            color = "black") +
  coord_polar("y", 
              start = 0, 
              direction = -1) +
  theme_void() +
  theme(legend.position = "FALSE") +
  labs(title = "Accidents with and without means of transport")
```

## Accidents according to the characteristics of the employee

### Management
From the graph below we can see that, the first bin `I` which represents employees in the industry and services sectors and they have the highest proportion of accidents 81% with respect to employees in the two other sectors, while employees in the agricultural sector `A` have the lowest rate of accidents, which is about 5% only. For the the employees who are working on behalf of the state `S` they have 14% of the accidents across Italy.


```{r}
# create a pie chart with slice labels
gestione <- Ita_Regions %>%
  count(Gestione) %>%
  arrange(desc(Gestione)) %>%
  mutate(prop = round(n*100/sum(n), 1),
         lab.ypos = cumsum(prop) - 0.5*prop)

gestione$label <- paste0(gestione$Gestione, "\n",
                         round(gestione$prop), "%")

ggplot(gestione, 
       aes(x = "", 
           y = prop, 
           fill = Gestione)) +
  geom_bar(width = 1, 
           stat = "identity", 
           color = "black") +
  geom_text(aes(y = lab.ypos, label = label), 
            color = "black") +
  coord_polar("y", 
              start = 0, 
              direction = -1) +
  theme_void() +
  theme(legend.position = "FALSE") +
  labs(title = "Accidents by Management")
```


### Accidents by tariff management
Looking at the figure below, The highest rate of accidents are coming from Non-Defined tariff management. However, 25% of the accidents are registered by tertiary sector, industrial sector contributes by 22% of the total accidents, handcraft activities have a rate of 12% and the least contributing sector is other activities with only 9% of the total accidents.




```{r}
G_Tariffaria <- Ita_Regions %>%
  count(GestioneTariffaria) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(G_Tariffaria, 
       aes(x = reorder(GestioneTariffaria, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "tariff management", 
       y = "Percent", 
       title  = "Accidents by tariff management")
```

### Accidents by large tariff group: code of the large tariff group

```{r}
Grande_Tariffaria <- Ita_Regions %>%
  count(GrandeGruppoTariffario) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(Grande_Tariffaria, 
       aes(x = reorder(GrandeGruppoTariffario, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "large tariff group", 
       y = "Percent", 
       title  = "Accidents by large tariff group")
```
From the above graph, agricultural processing and food and Non-Defined sector they contribute by the same proportion of accidents which is 36% fro each while wood and similar zero percent of accidents, furthermore the rate of accidents for metals and machinery, rock and glass mining and textiles and packaging only 1% for each sector.

## The number of accidents by economical sector ativity

```{r}
# create a treemap with tile labels
plotdata <- Ita_Regions %>%
  count(SettoreAttivitaEconomica)

ggplot(plotdata, 
       aes(fill = SettoreAttivitaEconomica, 
           area = n, 
           label = SettoreAttivitaEconomica)) +
  geom_treemap() + 
  geom_treemap_text(colour = "white", 
                    place = "centre") +
  labs(title = "Accidents by economical sector ativity") +
  theme(legend.position = "none")
```
```{r, results='hide'}
sort(prop.table(table(Ita_Regions$SettoreAttivitaEconomica)), decreasing = TRUE) #prop.table(table(Ita_Regions$SettoreAttivitaEconomica))
```

From the figure above we can see that 34.78 of the accidents are not identified as to which economical sector is belong. However, the sector with high proportion of accidents (0.0536) is Q86 `Assitenza Sanitaria` while the sector with the lowest proportion of accidents(0.000004%) is B07 `Estrazione di Minerali Metallifri`. Furthermore, `Commercio al dettalio (escluso quello di autoveicoli e di motocicli)` G47 has 0.04 contribution to the total number of accidents, while F43 `Lavori di costruzione specializzati` has 0.039 from the proportion of accidents. 

## The number of accidents by province

```{r}
# create a treemap with tile labels
plotprov <- Ita_Regions %>%
  count(LuogoAccadimento)

ggplot(plotprov, 
       aes(fill = LuogoAccadimento, 
           area = n, 
           label = LuogoAccadimento)) +
  geom_treemap() + 
  geom_treemap_text(colour = "white", 
                    place = "centre") +
  labs(title = "Accidents by province") +
  theme(legend.position = "none")
```
```{r, results='hide'}
sort(prop.table(table(Ita_Regions$LuogoAccadimento)), decreasing = TRUE)
```

The graph illustrate the number proportions of accidents by province, we can see that 0.065 of accidents are coming from 15 `province of Milan` which is the highest proportion of accidents compared to other provinces, the second highest proportion of accidents are occurred in 58 `Rom`e with proportion of accidents equals to 0.054, the third province with high proportion of accidents is 1 `Turin`, while the province with the lowest proportion of accidents is 94 `Isernia` which is about 0.00086, the second lowest proportion of accidents is occurred in 101 `Crotone` with proportion of accidents equals to 0.00115 and the third lowest frequent of accidents is coming from 102 `Vibo Valentia` whis is about 0.00124. However, the three province with the lowest frequency of accidents are located in south Italy while the province with high frequency of accidents are in the south and center of Italy.

# Analyses of impairment, indemnity, indemnified days
## Analyse of Indemnity

```{r}
idemnity <- Ita_Regions %>%
  count(Indennizzo) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(idemnity, 
       aes(x = reorder(Indennizzo, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Indemnity", 
       y = "Percent", 
       title  = "Participants by Indemnity")
```
```{r}
sort(prop.table(table(Ita_Regions$Indennizzo)), decreasing = TRUE)
```

The figure above illustrates the types of indemnity resulting from the accidents, which are `temporary`, `capital`, `direct annuity`and `survivors' annuity`. From the graph we can see that 52% of accidents indemnity are considered to be `TE` temporary, while 4% of the indemnity is considered as capital `CA` and 1% are going directly to annuity `RD` and about 0.1% are survivors' annuity `rs`. 

## Admministrative decision of the fatal outcome

```{r}
fetal <- Ita_Regions %>%
  count(DefinizioneAmministrativaEsitoMortale) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(fetal, 
       aes(x = reorder(DefinizioneAmministrativaEsitoMortale, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Indemnity", 
       y = "Percent", 
       title  = "Participants by Indemnity")
```


```{r}
sort(prop.table(table(Ita_Regions$DefinizioneAmministrativaEsitoMortale)), decreasing = TRUE)
```
The figure above shows the decisions about the accidents, which are `positive`, `negative` or `in investigation`. From the figure we analye that 99.78% of the accidents are not defined. However, the accidents with a fatal decision are the positive cases which is 0.125% of the total accidents, while the accidents that are not fatal which is the negative cases are 0.092% of the accidents and the accidents that its outcome are not decided yet `in invstigation` are 0.003% of the total accidents.



## Location of the accidents



# Total and permanent disability

Total permanent disability (TPD) is a condition in which an individual is no longer able to work due to injuries. Total permanent disability, also called permanent total disability, applies to cases in which the individual may never be able to work again.



## Degree of impairment > 60

```{r}
data(Ita_Regions)
GradoMenomazione_60 <- Ita_Regions[, c("GradoMenomazione","Indennizzo", "GiorniIndennizzati")] 

GradoMenomazione_60 <-  GradoMenomazione_60 %>%
                       filter(GradoMenomazione > 60)
```





The table below shows information about the degree of impairment when it is more than 60:
```{r}
reactable(GradoMenomazione_60, searchable = TRUE, minRows = 10)
```


```{r}
grad_60 <- GradoMenomazione_60 %>%
  count(Indennizzo) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(grad_60, 
       aes(x = reorder(Indennizzo, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Indennizzo", 
       y = "Percent", 
       title  = "Participants by Indennizzo")
```

The analysis of degree of impairment is crucial in defining the total and permanent disability, here if the insurance company based on this dataset decide to identify a person with degree of impairment greater than 60 as TPA, then from the table above we can see that 94% of the workers with degree of impairment greater than 60 are entitled to immediate annuity `RD`, which offers an immediate income to the annuitant, and 6% are entitled to survivors' annuity `DS`, which allows the annuitant to ensure after death, a continuous lifetime annuity for their dependents. 

To check if there is a relation between the days of compensation and indemnity a Biserial correlation test is applied.

```{r}
biserial.cor(GradoMenomazione_60$GiorniIndennizzati, GradoMenomazione_60$Indennizzo)
```

From the test we can see that there is almost no correlation between the days compensated and indemnity.

```{r}
ggplot(GradoMenomazione_60, 
       aes(x = factor(Indennizzo,
                      labels = c("Dirict annuity",
                                 "Survivors' annuity")), 
           y = GiorniIndennizzati, 
           color = Indennizzo)) +
  geom_boxplot(size=1,
               outlier.shape = 1,
               outlier.color = "black",
               outlier.size  = 3) +
  geom_jitter(alpha = 0.5, 
              width=.2) + 
  #scale_y_continuous(label = dollar) +
  labs(title = "Days of compensation according to indemnity",
       x = "",
       y = "") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()
```


## Degree of impairment > 40

```{r}
data(Ita_Regions)
GradoMenomazione_40 <- Ita_Regions[, c("GradoMenomazione","Indennizzo", "GiorniIndennizzati")] 

GradoMenomazione_40 <-  GradoMenomazione_40 %>%
                       filter(GradoMenomazione > 40)
```

The table below shows information about the degree of impairment when it is more than 60:

```{r}
reactable(GradoMenomazione_40, searchable = TRUE, minRows = 10)
```

```{r}
grad_40 <- GradoMenomazione_40 %>%
  count(Indennizzo) %>%
  mutate(pct = n / sum(n),
         pctlabel = paste0(round(pct*100), "%"))

# plot the bars as percentages, 
# in decending order with bar labels
ggplot(grad_40, 
       aes(x = reorder(Indennizzo, -pct),
           y = pct)) + 
  geom_bar(stat = "identity", 
           fill = "indianred3", 
           color = "black") +
  geom_text(aes(label = pctlabel), 
            vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(x = "Indennizzo", 
       y = "Percent", 
       title  = "Participants by Indennizzo")
```

The analysis of degree of impairment is crucial in defining the total and permanent disability, here if the insurance company based on this dataset decide to identify a person with degree of impairment greater than 40 as TPA, then from the table above we can see that 98% of the workers with degree of impairment greater than 40 are entitled to immediate annuity `RD`, which offers an immediate income to the annuitant, and 2% are entitled to survivors' annuity `DS`, which allows the annuitant to ensure after death, a continuous lifetime annuity for their dependents. However, when the insurance company decrease the threshold of the degree of impairment to 40, the number of persons defined as TPD is 2349, while when the threshold of the degree of impairment is 60, the number of persons defined as TPD is 856. 


```{r}
biserial.cor(GradoMenomazione_40$GiorniIndennizzati, GradoMenomazione_40$Indennizzo)
```

From the test we can see that there is almost no correlation between the days compensated and indemnity.
```{r}
ggplot(GradoMenomazione_40, 
       aes(x = factor(Indennizzo,
                      labels = c("Dirict annuity",
                                 "Survivors' annuity")), 
           y = GiorniIndennizzati, 
           color = Indennizzo)) +
  geom_boxplot(size=1,
               outlier.shape = 1,
               outlier.color = "black",
               outlier.size  = 3) +
  geom_jitter(alpha = 0.5, 
              width=.2) + 
  #scale_y_continuous(label = dollar) +
  labs(title = "Days of compensation according to indemnity",
       x = "",
       y = "") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()
```




